\announcesection{Algorithm Performance} 

\displayonelarge{Invariant Mass as a Discriminating Variable}
    { \footnotesize
        Choose two ``VBF Jets",
        then use their invariant mass
        as a discriminant in tagging.
    }
    {remote/figures/fig_mjj_null_mjj_distribution.pdf}


\displayonelarge{Performance Curves: Baseline}
    {Performance of $M_{jj}$ discriminant for events with two jets is not unreasonable.}
    {remote/performance/focused_perf_2only_roc_efficiency.pdf}

\displayonelarge{Performance Curves: Dealing with Three Jets}
    { \footnotesize
        With three jets, we need to decide which two are the VBF signal jets, and use these to calculate the $M_{jj}$ discriminant.

        \vspace{5mm}

        Naively, we can try picking the two leading $p_t$ jets. This drastically reduces performance.
    }
    {remote/performance/focused_perf_2-pt_roc_efficiency.pdf}

\displayonelarge{\small Two Measures of Performance: Tagging Efficiency VS Selection Efficiency}
    { \footnotesize
        Why do the leading $p_t$ jets perform so badly?

        \vspace{5mm}

        ...Well, how often are the leading $p_t$ jets actually the VBF jets?

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\
        \hline
        Leading $p_t$ & 53\% \\
        \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-pt_roc_efficiency.pdf}

\displayonelarge{Performance Curves: Worst Case Scenario}
    { \footnotesize
        How closely is selection efficiency related to tagging efficiency?

        Let's look at a worst case situation:
        What if the "VBF Jets" were chosen at random?

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\ \hline
        Leading $p_t$ & 53\% \\ \hline
        Random & 33\% \\ \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-pt-R_roc_efficiency.pdf}

\displayonelarge{Performance Curves: Best Case Scenario}
    { \footnotesize
        What about perfect selection efficiency?

        {\tiny CAUTION: Truth selection treats signal and background events \textit{differently};
        it is biasing the tagging performance and should be viewed only as an estimate}

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\ \hline
        Leading $p_t$ & 53\% \\ \hline
        Random & 33\% \\ \hline
        Truth & 100\% \\ \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-pt-R-T_roc_efficiency.pdf}

\displayonelarge{Performance Curves: A Better Approach}
    { \footnotesize
        A smarter approach is to use the jet pair which maximizes $M_{jj}$

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\ \hline
        Leading $p_t$ & 53\% \\ \hline
        Random & 33\% \\ \hline
        Truth & 100\% \\ \hline
        Max $M_{jj}$& 66\% \\ \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-pt-R-T-mjj_roc_efficiency.pdf}

\displayonelarge{Performance Curves: Introduce Machine Learning}
    { \footnotesize
        Enter Machine Learning... which seems to just be replicating $M_{jj}$ right now.
        I'm investigating ways to improve it.

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\ \hline
        Leading $p_t$ & 53\% \\ \hline
        Random & 33\% \\ \hline
        Truth & 100\% \\ \hline
        Max $M_{jj}$ & 66\% \\ \hline
        MLP & 66\% \\ \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-pt-R-T-mjj-mlp_roc_efficiency.pdf}

\displayonelarge{Performance Curves: What About a Better Tagger?}
    { \footnotesize
        A machine-learning-based tagger easily outperforms the $M_{jj}$-based tagger.

        \vspace{5mm}

        \begin{tabular}{|c|c|}\hline
        Algorithm & Efficiency \\ \hline
        Leading $p_t$ & 53\% \\ \hline
        Random & 33\% \\ \hline
        Truth & 100\% \\ \hline
        Max $M_{jj}$ & 66\% \\ \hline
        MLP & 66\% \\ \hline
        \end{tabular}
    }
    {remote/performance/focused_perf_2-mjj-mlp_NN_roc_efficiency.pdf}

\displayonelarge{Performance Curves: Overall Performance}
    {
        If we look at the combined performance of 2 and 3 jet events,
        the difference is not dramatic, but there is still room for improvement.

    }
    {remote/performance/focused_perf_2-3-summary_roc_efficiency.pdf}
