% -- Official people --
Embarking upon a graduate degree in physics is a daunting task,
    one which is impossible without extensive help along the way.
% Steve
First and foremost I want to thank my adviser Stephen Sekula.
It cannot be overstated how much better my graduate career has been
    thanks to his unwavering mentorship and compassion.
His constant support helped me overcome countless challenges,
    and his cheeful attitude ensured that I had genuine fun
    with my research all the way through to my graduation.
% Comittee
I want to thank my thesis committee members,
    Roberto Vega, Jingbo Ye, and Chris Pollard,
    for their valuable feedback and guidance towards the completion of my research.
% SMU Atlas group
I also want to thank the SMU ATLAS group for their regular feedback and research suggestions.
% esp. Katherine and Alessandra
Special thanks go to Katherine Laney and Alessandra Betti
    for all their help getting me started with my analysis group
    and in helping me address challenges within my research.
% SLAC ATLAS group in general
I would like to thank the SLAC ATLAS group as well,
    for so kindly welcoming me as a member for the year I was there.
% Ariel Schwartzmann (got me started on VBF)
In particular I want to thank Ariel Schwartzmann for hosting me
    and for starting my journey with Vector Boson Fusion.
% and Larry Ruckman
Additionally I want to thank Larry Ruckman,
    who oversaw me as I worked with electronics testing and firmware design.
Working with him was an invaluable experience
    and I appreciate the patience he had as I learned to operate in such a new environment.
% 4b group
Of course, I also wish to thank the di-Higgs 4b analysis group.
I never could have understood all the different aspects of this analysis without the incredible amount of help
    every member of the group was willing to provide.


% -- Less formal SMU people --
As well as all of my ATLAS and research colleagues,
    there are numerous people at Southern Methodist Unviversity that made my time here immeasurably better.
% Fellow grad students 
All of my fellow physics graduate students have been a constant source of community, support, and friendship
    through our shared struggle through the degree.
% (esp. Jing and James)
I especially need to thank the two other students of my class, James and Jing.
I would have failed out of SMU several times over were it not
    for all their help throughout our classes and homework assignments.
% Matthew Feickert
I also want to pay special note to Matthew Feickert not only for being a generally good friend and colleague,
    but in particular for putting together the Latex template\cite{dedman_latex_git} used for this thesis.
Furthermore, Matthew's own thesis\cite{matthew_feickert} is a beautiful example of what a thesis should be,
    and has served as a constant template and metric by which I could measure my own progress
    (indeed, this very section is structured based on his example).
% Lacey and Michele
Of course, I also need to thank the backbone of the SMU physics department, 
    Lacey (who has since departed for greener pastures) and Michelle.
Their commitment to navigating the bureaucratic and financial labyrinth of the SMU graduate program
    has been a true life-saver, and I dread to think of how I would have handled it all on my own.


% -- Even less formal people --
Lastly, I want to express my deepest gratitude to my friends, family, and mentors.
% Undergrad advisors? (Bruce got me started with physics research, Vitaliy got me into SMU)
Bruce Schuum from UCSC was my first research adviser
    and the first to show me how rewarding physics research could be.
Also from UCSC, Vitaliy Fadeyev introduced me to electronics testing
    and, crucially, I owe my enrollment into SMU to his advice and assistance.
% Rebecca and Aaron (esp. b/c she helped pick me up after the qual beat me down)
Moving outside of academia, I need to take a moment to pay special thanks
    to my good friends Rebecca and Aaron.
In addition to being amazing friends, they were there to pick me up
    at my absolute lowest point in graduate school.
% Danny (comp sci guru; introduced me to linux)
I also want to thank my long-time university friend Danniel Bittman.
We struggled together through nearly every undergraduate physics course we had,
    and he introduced me to the world of Linux and programming,
    teaching me lessons which have proved invaluable throughout my graduate career.

% Parents
To my mom and dad, Anita and Rick, there is really no way to even begin to do justice
    to how much credit and thanks you each deserve.
I could not have asked for better parents,
    and I never would have made it this far without your endless love and support.
% Kanananananananananananananananananananananananannananananananana
And finally, I want to thank my most wonderful and adorable
    fianc\'e Kana\footnote{nananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananananana}.
You have brought peace and joy into what should have otherwise been
    some of the most stressful years of my life.
More importantly, as I close out this chapter of my life I have spent so long pursuing,
    you have given me clarity and purpose as to where I go from here.
Though I dedicate this thesis to a friend,
    I dedicate the rest of my life to you.
